---
title: "MetaAwarness - Experiment 3 - Task 1"
author: "Adam Barnas"
date: "Last compiled at `r format(Sys.time(), '%l:%M %p')` on `r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    code_folding: show
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: no
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up R environment.

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(plyr)
library(magick)
library(png)
library(lme4)
library(lmerTest)
library(irrNA)
library(psy)
library(coefficientalpha)
library(parameters)
library(dplyr)
```

# Written descriptions of changes.

## Rensink.

### Read-in datafiles.

```{r}
rensink_semantic_round_1 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Rensink/Descriptions/rensink_semantic_round_1.csv", col_types = cols())
rensink_semantic_round_2 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Rensink/Descriptions/rensink_semantic_round_2.csv", col_types = cols())
rensink_semantic_round_3 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Rensink/Descriptions/rensink_semantic_round_3.csv", col_types = cols())

rensink_semantic_all<- rbind(rensink_semantic_round_1, rensink_semantic_round_2, rensink_semantic_round_3)
rensink_semantic_all <- rensink_semantic_all %>% 
  filter(image != 'airplane' & image != 'cow')
```

Count subjects.

```{r}
nrow(rensink_semantic_all %>% distinct(workerId,.keep_all = FALSE))
```

### Get initial count of descriptions for each image.

``` {r}
rensink_semantic_all_count <- rensink_semantic_all %>% 
  group_by(workerId,image) %>% 
  dplyr::summarize(counts = n()) %>%
  spread(image,counts) %>%
  mutate(sum = rowSums(.[-1], na.rm = TRUE))

rensink_semantic_all_count <- data.frame(count = colSums(rensink_semantic_all_count[,2:49], na.rm = TRUE))
rensink_semantic_all_count <- tibble::rownames_to_column(rensink_semantic_all_count, "image")
rensink_semantic_all_count
```

### Filter good subjects.

```{r message=FALSE}
rensink_semantic_good <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Analyses/Rensink_Semantic_good.csv")
rensink_semantic_final_descriptions <- rensink_semantic_all %>% 
      filter(rensink_semantic_all$workerId %in% rensink_semantic_good$workerId)
```

Count good subjects

```{r}
nrow(rensink_semantic_final_descriptions %>% distinct(workerId,.keep_all = FALSE))
```

### Filter and count bad subjects.

```{r}
rensink_semantic_bad_descriptions <- rensink_semantic_all %>% 
      filter(!rensink_semantic_all$workerId %in% rensink_semantic_good$workerId)
nrow(rensink_semantic_bad_descriptions %>% distinct(workerId,.keep_all = FALSE))
```

### Get final count of descriptions for each image.

```{r}
rensink_semantic_final_descriptions_count <- rensink_semantic_final_descriptions %>% 
  group_by(workerId,image) %>% 
  dplyr::summarize(counts = n()) %>%
  spread(image,counts) %>%
  mutate(sum = rowSums(.[-1], na.rm = TRUE))

rensink_semantic_final_descriptions_count <- data.frame(count = colSums(rensink_semantic_final_descriptions_count[,2:49], na.rm = TRUE))
rensink_semantic_final_descriptions_count <- tibble::rownames_to_column(rensink_semantic_final_descriptions_count, "image")
rensink_semantic_final_descriptions_count
rensink_semantic_final_descriptions_count$stim_set <- "rensink"
```

This is a frequency distrubtion of the number of descriptions.

```{r}
descriptions_rensink_freq <- data.frame(table(rensink_semantic_final_descriptions_count$count))
colnames(descriptions_rensink_freq) <- c("count", "frequency")
descriptions_rensink_freq 
```

## Ma.

### Read-in datafiles.

```{r}
ma_semantic_round_1 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Ma/Descriptions/ma_semantic_round_1.csv", col_types = cols())
ma_semantic_round_2 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Ma/Descriptions/ma_semantic_round_2.csv", col_types = cols())
ma_semantic_round_3 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Ma/Descriptions/ma_semantic_round_3.csv", col_types = cols())

ma_semantic_all<- rbind(ma_semantic_round_1, ma_semantic_round_2, ma_semantic_round_3)
ma_semantic_all <- ma_semantic_all %>% 
  filter(image != 'airplane' & image != 'cow')
```

Count subjects.

```{r}
nrow(ma_semantic_all %>% distinct(workerId,.keep_all = FALSE))
```

### Get initial count of descriptions for each image.

``` {r}
ma_semantic_all_count <- ma_semantic_all %>% 
  group_by(workerId,image) %>% 
  dplyr::summarize(counts = n()) %>%
  spread(image,counts) %>%
  mutate(sum = rowSums(.[-1], na.rm = TRUE))

ma_semantic_all_count <- data.frame(count = colSums(ma_semantic_all_count[,2:70], na.rm = TRUE))
ma_semantic_all_count <- tibble::rownames_to_column(ma_semantic_all_count, "image")
ma_semantic_all_count
```

### Filter good subjects.

```{r message=FALSE}
ma_semantic_good <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Analyses/Ma_Semantic_good.csv")
ma_semantic_final_descriptions <- ma_semantic_all %>% 
      filter(ma_semantic_all$workerId %in% ma_semantic_good$workerId)
```

Count good subjects

```{r}
nrow(ma_semantic_final_descriptions %>% distinct(workerId,.keep_all = FALSE))
```

### Filter and count bad subjects.

```{r}
ma_semantic_bad_descriptions <- ma_semantic_all %>% 
      filter(!ma_semantic_all$workerId %in% ma_semantic_good$workerId)
nrow(ma_semantic_bad_descriptions %>% distinct(workerId,.keep_all = FALSE))
```

### Get final count of descriptions for each image.

```{r}
ma_semantic_final_descriptions_count <- ma_semantic_final_descriptions %>% 
  group_by(workerId,image) %>% 
  dplyr::summarize(counts = n()) %>%
  spread(image,counts) %>%
  mutate(sum = rowSums(.[-1], na.rm = TRUE))

ma_semantic_final_descriptions_count <- data.frame(count = colSums(ma_semantic_final_descriptions_count[,2:70], na.rm = TRUE))
ma_semantic_final_descriptions_count <- tibble::rownames_to_column(ma_semantic_final_descriptions_count, "image")
ma_semantic_final_descriptions_count
ma_semantic_final_descriptions_count$stim_set <- "ma"
```

This is a frequency distrubtion of the number of descriptions.

```{r}
descriptions_ma_freq <- data.frame(table(ma_semantic_final_descriptions_count$count))
colnames(descriptions_ma_freq) <- c("count", "frequency")
descriptions_ma_freq 
```

## Wolfe1.

### Read-in datafiles.

```{r}
wolfe1_semantic_round_1 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe1/Descriptions/wolfe1_semantic_round_1.csv", col_types = cols())
wolfe1_semantic_round_2 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe1/Descriptions/wolfe1_semantic_round_2.csv", col_types = cols())
wolfe1_semantic_round_3 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe1/Descriptions/wolfe1_semantic_round_3.csv", col_types = cols())
wolfe1_semantic_round_4 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe1/Descriptions/wolfe1_semantic_round_4.csv", col_types = cols())

wolfe1_semantic_all<- rbind(wolfe1_semantic_round_1, wolfe1_semantic_round_2, wolfe1_semantic_round_3, wolfe1_semantic_round_4)
wolfe1_semantic_all <- wolfe1_semantic_all %>% 
  filter(image != 'airplane' & image != 'cow')
```

Count subjects.

```{r}
nrow(wolfe1_semantic_all %>% distinct(workerId,.keep_all = FALSE))
```

### Get initial count of descriptions for each image.

``` {r}
wolfe1_semantic_all_count <- wolfe1_semantic_all %>% 
  group_by(workerId,image) %>% 
  dplyr::summarize(counts = n()) %>%
  spread(image,counts) %>%
  mutate(sum = rowSums(.[-1], na.rm = TRUE))

wolfe1_semantic_all_count <- data.frame(count = colSums(wolfe1_semantic_all_count[,2:112], na.rm = TRUE))
wolfe1_semantic_all_count <- tibble::rownames_to_column(wolfe1_semantic_all_count, "image")
wolfe1_semantic_all_count
```

### Filter good subjects.

```{r message=FALSE}
wolfe1_semantic_good <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Analyses/Wolfe1_Semantic_good.csv")
wolfe1_semantic_final_descriptions <- wolfe1_semantic_all %>% 
      filter(wolfe1_semantic_all$workerId %in% wolfe1_semantic_good$workerId)
```

Count good subjects

```{r}
nrow(wolfe1_semantic_final_descriptions %>% distinct(workerId,.keep_all = FALSE))
```

### Filter and count bad subjects.

```{r}
wolfe1_semantic_bad_descriptions <- wolfe1_semantic_all %>% 
      filter(!wolfe1_semantic_all$workerId %in% wolfe1_semantic_good$workerId)
nrow(wolfe1_semantic_bad_descriptions %>% distinct(workerId,.keep_all = FALSE))
```

### Get final count of descriptions for each image.

```{r}
wolfe1_semantic_final_descriptions_count <- wolfe1_semantic_final_descriptions %>% 
  group_by(workerId,image) %>% 
  dplyr::summarize(counts = n()) %>%
  spread(image,counts) %>%
  mutate(sum = rowSums(.[-1], na.rm = TRUE))

wolfe1_semantic_final_descriptions_count <- data.frame(count = colSums(wolfe1_semantic_final_descriptions_count[,2:112], na.rm = TRUE))
wolfe1_semantic_final_descriptions_count <- tibble::rownames_to_column(wolfe1_semantic_final_descriptions_count, "image")
wolfe1_semantic_final_descriptions_count
wolfe1_semantic_final_descriptions_count$stim_set <- "wolfe1"
```

This is a frequency distrubtion of the number of descriptions.

```{r}
descriptions_wolfe1_freq <- data.frame(table(wolfe1_semantic_final_descriptions_count$count))
colnames(descriptions_wolfe1_freq) <- c("count", "frequency")
descriptions_wolfe1_freq 
```

## Wolfe2.

### Read-in datafiles.

```{r}
wolfe2_semantic_round_1 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe2/Descriptions/wolfe2_semantic_round_1.csv", col_types = cols())
wolfe2_semantic_round_2 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe2/Descriptions/wolfe2_semantic_round_2.csv", col_types = cols())
wolfe2_semantic_round_3 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe2/Descriptions/wolfe2_semantic_round_3.csv", col_types = cols())
wolfe2_semantic_round_4 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe2/Descriptions/wolfe2_semantic_round_4.csv", col_types = cols())
wolfe2_semantic_round_5 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe2/Descriptions/wolfe2_semantic_round_5.csv", col_types = cols())
wolfe2_semantic_round_6 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe2/Descriptions/wolfe2_semantic_round_6.csv", col_types = cols())
wolfe2_semantic_round_7 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe2/Descriptions/wolfe2_semantic_round_7.csv", col_types = cols())
wolfe2_semantic_round_8 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe2/Descriptions/wolfe2_semantic_round_8.csv", col_types = cols())
wolfe2_semantic_round_9 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe2/Descriptions/wolfe2_semantic_round_9.csv", col_types = cols())
wolfe2_semantic_round_10 <- read_csv("/Volumes/Files/Box/Archive/Predicting_ChangeBlindness/Raw_Data/Wolfe2/Descriptions/wolfe2_semantic_round_10.csv", col_types = cols())


wolfe2_semantic_all<- rbind(wolfe2_semantic_round_1, wolfe2_semantic_round_2, wolfe2_semantic_round_3, wolfe2_semantic_round_4, wolfe2_semantic_round_5, wolfe2_semantic_round_6, wolfe2_semantic_round_7, wolfe2_semantic_round_8, wolfe2_semantic_round_9, wolfe2_semantic_round_10)
wolfe2_semantic_all <- wolfe2_semantic_all %>% 
  filter(image != 'airplane' & image != 'cow')
```

Count subjects.

```{r}
nrow(wolfe2_semantic_all %>% distinct(workerId,.keep_all = FALSE))
```

### Get initial count of descriptions for each image.

``` {r}
wolfe2_semantic_all_count <- wolfe2_semantic_all %>% 
  group_by(workerId,image) %>% 
  dplyr::summarize(counts = n()) %>%
  spread(image,counts) %>%
  mutate(sum = rowSums(.[-1], na.rm = TRUE))

wolfe2_semantic_all_count <- data.frame(count = colSums(wolfe2_semantic_all_count[,2:255], na.rm = TRUE))
wolfe2_semantic_all_count <- tibble::rownames_to_column(wolfe2_semantic_all_count, "image")
wolfe2_semantic_all_count
```

### Filter good subjects.

```{r message=FALSE}
wolfe2_semantic_good <- read_csv("/Volumes/Files/Box/MetaAwareness/data/wolfe2_Semantic_good.csv")
wolfe2_semantic_final_descriptions <- wolfe2_semantic_all %>% 
      filter(wolfe2_semantic_all$workerId %in% wolfe2_semantic_good$workerId)
```

Count good subjects

```{r}
nrow(wolfe2_semantic_final_descriptions %>% distinct(workerId,.keep_all = FALSE))
```

### Filter and count bad subjects.

```{r}
wolfe2_semantic_bad_descriptions <- wolfe2_semantic_all %>% 
      filter(!wolfe2_semantic_all$workerId %in% wolfe2_semantic_good$workerId)
nrow(wolfe2_semantic_bad_descriptions %>% distinct(workerId,.keep_all = FALSE))
```

### Get final count of descriptions for each image.

```{r}
wolfe2_semantic_final_descriptions_count <- wolfe2_semantic_final_descriptions %>% 
  group_by(workerId,image) %>% 
  dplyr::summarize(counts = n()) %>%
  spread(image,counts) %>%
  mutate(sum = rowSums(.[-1], na.rm = TRUE))

wolfe2_semantic_final_descriptions_count <- data.frame(count = colSums(wolfe2_semantic_final_descriptions_count[,2:255], na.rm = TRUE))
wolfe2_semantic_final_descriptions_count <- tibble::rownames_to_column(wolfe2_semantic_final_descriptions_count, "image")
wolfe2_semantic_final_descriptions_count
wolfe2_semantic_final_descriptions_count$stim_set <- "wolfe2"
```

This is a frequency distrubtion of the number of descriptions.

```{r}
descriptions_wolfe2_freq <- data.frame(table(wolfe2_semantic_final_descriptions_count$count))
colnames(descriptions_wolfe2_freq) <- c("count", "frequency")
descriptions_wolfe2_freq 
```

## Combined analyses.

Initial sample size.

```{r}
nrow(rensink_semantic_all %>% distinct(workerId,.keep_all = FALSE)) + nrow(ma_semantic_all %>% distinct(workerId,.keep_all = FALSE)) + nrow(wolfe1_semantic_all %>% distinct(workerId,.keep_all = FALSE)) + nrow(wolfe2_semantic_all %>% distinct(workerId,.keep_all = FALSE))
```

Number of excluded subjects due to poor descriptions on catch trials.

```{r}
nrow(rensink_semantic_bad_descriptions %>% distinct(workerId,.keep_all = FALSE)) + nrow(ma_semantic_bad_descriptions %>% distinct(workerId,.keep_all = FALSE)) + nrow(wolfe1_semantic_bad_descriptions %>% distinct(workerId,.keep_all = FALSE)) + nrow(wolfe2_semantic_bad_descriptions %>% distinct(workerId,.keep_all = FALSE))
```

Count good subjects

```{r}
nrow(rensink_semantic_final_descriptions %>% distinct(workerId,.keep_all = FALSE)) + nrow(ma_semantic_final_descriptions %>% distinct(workerId,.keep_all = FALSE)) + nrow(wolfe1_semantic_final_descriptions %>% distinct(workerId,.keep_all = FALSE)) + nrow(wolfe2_semantic_final_descriptions %>% distinct(workerId,.keep_all = FALSE))
```

```{r}
descriptions <- rbind(rensink_semantic_final_descriptions_count, ma_semantic_final_descriptions_count, wolfe1_semantic_final_descriptions_count, wolfe2_semantic_final_descriptions_count)
```

This is the average number of descriptions for all 480 image pairs.

```{r}
mean(descriptions$count)
sd(descriptions$count)
range(descriptions$count)
```

This is a frequency distrubtion of the number of descriptions for all 482 image pairs. For example, 1 image pair had 3 descriptions, 166 image pairs had 4 descriptions, etc.

```{r}
descriptions_frequency_all <- data.frame(table(descriptions$count))
colnames(descriptions_frequency_all) <- c("count", "frequency")
descriptions_frequency_all 
```

This is the average number of descriptions for image pairs in each stimulus set.

```{r}
descriptions_average <- descriptions %>%
  group_by(stim_set) %>%
  dplyr::summarize(average = mean(count)) %>%
  spread(stim_set,average)
descriptions_average 
```